Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-04-22 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex

The distribution into all-atom  (AA) and united-atom (UA) parts within the lipids is the same
as in the original CHARMM27-UA model by H\'enin et al.~\cite{henin08}.  
This distribution differs from the one by Lee-C36-UA because  in Botan's model, C22 and C32 and 
their hydrogens are merged into  united atoms, whereas in Lee's model their hydrogens are described explicitely.
The  united-atom Berger model ~\cite{berger97} was used for the tails and the UA-AA interactions as in Ref. ~\citenum{henin08}. 
The difference between this model and the original one by H\'enin~\cite{henin08} is the replacement of the 
AA parameters for the heads by  the parameters of the all-atom
 CHARMM36 force-field~\cite{klauda10}. Contrarily to the model by Lee et al.~\cite{lee14}, no reparametrization was done.

>>>>

The distribution into all-atom  (AA) and united-atom (UA) parts within the lipids is the same
as in the original CHARMM27-UA model by H\'enin et al.~\cite{henin08}.  
This distribution differs from the one by Lee-CHARMM36-UA model solely
for the first methylene groups of the two acyl chains (C22 and C32 in CHARMM36 topology): 
their hydrogens are merged into  united atoms, whereas in Lee's model their hydrogens are described explicitely.
The  united-atom Berger model ~\cite{berger97} was used for the tails and the UA-AA interactions as in Ref. ~\citenum{henin08}. 
The difference between this model and the original one by H\'enin~\cite{henin08} is the replacement of the 
AA parameters for the heads by  the parameters of the all-atom
 CHARMM36 force-field~\cite{klauda10}. Contrarily to the model by Lee et al.~\cite{lee14}, no reparametrization was done.
